LAGOS lake depth

### 2021-08-12 tables/01_predictors.Rmd
add word output

if(interactive()){
  clipr::write_clip(
    gsub("%\\*\\*", "\\\\%\\*\\*",
    gsub("_", "\\\\_",
    gsub("%\\\\", "\\\\%\\\\",
    sub("\\\\midrule", "\\\\hline",
    sub("\\\\bottomrule", "\\\\hline",
    sub("\\\\toprule", "\\\\hline",
        knitr::kable(dt, digits = 2, format = "latex",
       booktabs = TRUE, linesep = "", align = c("l"), escape = FALSE)))))))
     )
}
```

>>>>

if(interactive()){
  clipr::write_clip(
    gsub("%\\*\\*", "\\\\%\\*\\*",
    gsub("_", "\\\\_",
    gsub("%\\\\", "\\\\%\\\\",
    sub("\\\\midrule", "\\\\hline",
    sub("\\\\bottomrule", "\\\\hline",
    sub("\\\\toprule", "\\\\hline",
        knitr::kable(dt, digits = 2, format = "latex",
       booktabs = TRUE, linesep = "", align = c("l"), escape = FALSE)))))))
     )
}

# ---- Word output ----

# flextable::save_as_docx(flextable::flextable(dt), path = "../manuscript/inland_waters/table1.docx")
```

### 2021-08-12 tables/02_model_metrics.Rmd
add word output

# clipr::write_clip(
#   knitr::kable(dt_metrics, format = 'latex', align = c("llll"),
# escape = TRUE))
```

>>>>

# clipr::write_clip(
#   knitr::kable(dt_metrics, format = 'latex', align = c("llll"),
# escape = TRUE))
# flextable::save_as_docx(flextable::flextable(dt_metrics), path = "../manuscript/inland_waters/table2.docx")
```
